Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-09-29 manuscript.Rmd
Updates...
Updated descriptives for the first section.

n.so.yr <- left_join(n.so, n.yr) %>%
    group_by(title) %>%
    summarise(first = min(year), last = max(year), n = n()) %>%
    arrange(desc(n))

@@

```{r Figure 1 Small Multiples Paper}

>>>>

n.so.yr <- left_join(n.so, n.yr) %>%
    group_by(title) %>%
    summarise(first = min(year), last = max(year), n = n()) %>%
    arrange(desc(n)) %>%
    rename(Journal = title)

table1 <- left_join(n.so.yr, abb.df) %>%
  select(-X) %>%
  select(Journal, Abbrev, n, first, last)

sum_Articles <- sum(table1$n)
median_Articles <- median(table1$n)
mean_Articles <- mean(table1$n)
sd_Articles <- sd(table1$n)

@@

```{r Figure 1 Small Multiples Paper}
scopus.df < scopus.df %>% filter(Year <= 2013)
